---
pagetitle: "About Me"
output: 
  html_document
---
<!--
<style>
.main-container {
  width: auto;
  max-width: 700 !important;
  margins: auto;
}
</style>



good themes: Good ones: simplex, yeti, lumen
<body style="width:50%;align:center">
Best websites for building rmarkdown github pages:
https://jules32.github.io/rmarkdown-website-tutorial/basic_workflow.html
https://bookdown.org/yihui/rmarkdown/html-document.html#appearance_and_style
Icons: https://fontawesome.com/v4.7.0/cheatsheet/
https://holtzy.github.io/Pimp-my-rmd/
--> 


```{css, echo=FALSE}

# this adjusts the current page

body .main-container {
  max-width: 700px !important;
  width: 700px !important;
}
body {
  max-width: 700px !important;
}
a:hover img {
  opacity: 1;
  filter: alpha(opacity=100);
}
```




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=T)
```

```{r initiate, include=FALSE}
source("scripts/00_functions.R")
source("scripts/welcome_page.R")
```

<br>
<br>
<p><b style="opacity:0.8">
*I believe the fundamental beauty of the world comes from understanding the stories behind the patterns we see—and that is what I seek as a data scientist. I eat, sleep, and breathe managing, analyzing, visualizing, and presenting data. Have some data? Let me clean it. Have some numbers? Let me tell a story.*
<br>
</b></p>

<a href="personal-scrape.html" style="border:0;">
```{r echo=F, fig.height=4.5}
  dat <- amazon_books
  years <- unique(year(dat$order_date))
  years <- c(years,"2020")
  jan1year <- as.Date(paste(years,01,01,sep="-"))
  total=nrow(dat)
  
  par(mai=c(1.1,1.3,.3,.2))
  plot(data=dat, cum_total~order_date, type="n", axes=F, ylab="",xlab="", xlim=c(min(jan1year),as.Date("2020-01-01")),
       main="", ylim=c(0,240))
  axis(1, at=jan1year,labels=years, las=2, cex=.5, cex=.5)
  axis(2, at=seq(0,200,50),labels=seq(0,200,50), las=2)
  polygon(x=c(dat$order_date, rev(dat$order_date)), y=c(dat$cum_total,rep(0,total)),
          border=F, col=t_col("darkgreen",50))
  mtext("Year",side=1, line=3.5, cex=1.2)
  mtext("Number of Books\nPurchased",side=2, line=3, cex=1.2)
  
  #mtext(side=3, cex=1.4,"Luka Negoita:", font=2, adj=0, line=1.1)
  
  arrows(x0=as.Date("2011-06-06"), x1=as.Date("2011-06-06"), y0=0, y1=70, length=.1, lwd=2) # graduated college
  text("B.A. in Human Ecology", x=as.Date("2011-06-06"), y=80, adj=.9, cex=.7)
  
  arrows(x0=as.Date("2012-08-16"), x1=as.Date("2012-08-16"), y0=0, y1=105, length=.1, lwd=2) # graduated college
  text("Started grad school", x=as.Date("2012-08-16"), y=115, adj=.9, cex=.7)
  
  arrows(x0=as.Date("2014-10-16"), x1=as.Date("2014-10-16"), y0=0, y1=150, length=.1, lwd=2) # graduated college
  text("Passed the qualifying exam", x=as.Date("2014-10-16"), y=160, adj=.9, cex=.7)
  
  arrows(x0=as.Date("2018-05-13"), x1=as.Date("2018-05-13"), y0=0, y1=200, length=.1, lwd=2) # graduated college
  text("Ph.D. in Ecology", x=as.Date("2018-05-13"), y=210, adj=.9, cex=.7)
  
  arrows(x0=as.Date("2019-04-10"), x1=as.Date("2019-04-10"), y0=0, y1=225, length=.1, lwd=2) # graduated college
  text("Moved to Galápagos", x=as.Date("2019-04-10"), y=235, adj=.9, cex=.7)

```
</a>
<div class="caption">

My Amazon book purchase history and how it relates to some major life events.

</div>


<!--
```{r include=FALSE}
jobs <- c("Ecologist and Biostatistician\nCharles Darwin Foundation, Galapagos Islands, Ecuador","Freelance Data Scientist","Senior Research Analyst\nThe Research Foundation for SUNY, Syracuse, NY","Founder and CEO\nHabitU Lab, LLC, Syracuse, NY")
roles <- c("• Designed research studies and analyzed environmental data using Bayesian, regression, model selection, and time-series analysis to improve the success of environmental conservation programs\n• Generated data visualizations, infographics, and technical reports for communicating results to stakeholders and general public\n• Built a culture of learning by bringing staff together in joint educational and community-building experiences\n• Built and maintained online dashboards with R-Shiny for managing, visualizing, and analyzing financial and ecological data",
"•Led four major research programs at two universities, executing all technical design, data collection, and data analyses\n•Funded ten grants, fellowships, or crowdfunds totaling over $175,000\n•Designed the research for a study to test effectiveness of an app designed to help people reduce stress\n•Published three peer-reviewed publications and numerous conference presentations and technical reports
", 
"•Conducted statistical analyses on environmental data from studies completed in the Galapagos islands\n•Generated graphical and tabular summaries of analyses, and produced narrative of the statistical methods and interpretations of results",
"•Led a development team to build an app designed to help people reduce stress by combining a habit-tracking system with behavioral psychology\n•Bootstrapped the tech startup through early growth stages by using the lean startup philosophy, consulting with mentors, and participating in business incubators and competitions.")
test <- tibble(jobs,roles)
```

```{r}
#pander::pander(test, justify="left")
```


<div class="column-left">

### Experience

<b>Oct 2017 – Current</b>

<b>May 2010 – May 2018</b>

<b>Dec 2017 – Mar 2018</b>

<b>Sept 2015 – Jan 2018</b>

```{r}
#head(mtcars)
```
</div>
--> 

